Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-10 Docs/Paper/LaTex/template.tex
fix references

\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction ~\cite{Baier2008}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}. Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors. Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner. The system models are accompanied by algorithms that systematically explore all the states of the system model.}

@@

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3. All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.

@@

\comment{
Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior ~\cite{Baier2008}, ~\cite{Clarke2009}. These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry. However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}. Much research has been devoted to mitigate this problem.
}

@@

The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less~\cite{Biere2009}. To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Armando2009},\cite{Ganai2006},\cite{Cordeiro2012}.

@@

Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}. A $\nu$Z logical context must firstly be created (line $02$), in order to add constraints and to check whether a given model exists to the set of constraints. Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.

@@

%3
\bibitem{Baier2008}
Baier, C., Katoen, J-P (2008), ``{Principles of Model Checking}'', The MIT Press, London.

%4
\bibitem{Clarke2009}
Clarke, E., Emerson, E., Sifakis, J. (2009), ``{Model checking: algorithmic verification and debugging},'' In: Communications of the Association Computing Machinery, v. 52, n. 11, pp. 74--84.

%5
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).

%5
\bibitem{Trindade2016}
Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%6
\bibitem{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. (2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc. of the Intl. Conf. on Software Engineering and Service Science, pp. 921--924.

%8
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.

@@

%10
\bibitem{Biere2009}
Biere, A. (2009), ``{Bounded model checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.

%11
\bibitem{Clarke2004}
Clarke, E., Kroening, D., Lerda, F. (2004), ``{A Tool for Checking ANSI-C Programs}'', In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 2988, pp. 168--176.

%12
\bibitem{Armando2009}
Armando, A., Mantovani, J., Platania, L. (2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl. Journal on Software Tools for Technology Transfer, v. 11, n. 1, pp. 69--83.

%13
\bibitem{Ganai2006}
Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.

%14
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based bounded model checking for embedded ANSI-C software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

%15
\bibitem{Cordeiro2011}
Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.

%16
\bibitem{Ramalho2013}
Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. (2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl. Conf. and Workshops on the Engineering of Computer-Based Systems, pp. 147--156.

%17
\bibitem{Teich2012}
Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.

%18
\bibitem{TheMathWorks2013}
The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.

%19
\bibitem{Tranquillo2011}
Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.

%20
\bibitem{Hong2010}
Hong, L., Cai, J. (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc. of the Intl. Conf. on Computer and Automation Engineering, pp. 185--189.

%21
\bibitem{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc. of the annual workshop on workload characterization, pp. 3--14.

%22
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.

%23
\bibitem{Dagum1998}
Dagum, L., Menon, R. (1998), ``{OpenMP: an industry-standard API for shared-memory programming.},'' In: Proc. of the Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.

%24
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.

%25
\bibitem{Brummayer2009}
Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp. 174-–177.

%26
\bibitem{Barrett2011}
Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 6806, pp. 171--177.

%27
\bibitem{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. (2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v. 35, n. 1-3, pp. 265--293.

%28
\bibitem{Dutertre2014}
Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.

%29
\bibitem{Holzmann2011}
Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.

%30
\bibitem{Holzmann2012}
Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.

%31
\bibitem{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.

%32
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%33
\bibitem{Qawasmeh2014}
Qawasmeh, A., Malik, A., Chapman, B. (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc. of the Intl. Symp. on Parallel \& Distributed processing, pp. 1049--1058.

%34
\bibitem{Bjorner2014}
Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.

%35
\bibitem{OpenMP1998}
OpenMP Architecture Review Board, OpenMP C and C++
Application Pogram Interface, Version 1.0, October 1998.
http://www.openmp.org

%36
\bibitem{Z3API}
Magellan, ``{Source code and documentation},''
  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.

%37
\bibitem{GA}
URFJ, ``{Algoritmos Genéticos: Fundamentos e Aplicações. Marcio Nunes de Miranda},''
  \url{http://www.nce.ufrj.br/GINAPE/VIDA/alggenet.htm}, Accessed 18th August 2015.

%38
\bibitem{NarodytskaN}
Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.

%39
\bibitem{Federica2008}
Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc. of the Intl. Conf. on Service-Oriented Computing, LNCS 5364, pp. 116--131

%40
\bibitem{Barth1995}
Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.

%41
\bibitem{Vasco2005}
Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.

%42
\bibitem{Pavlinovic2015}
Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.

%43
\bibitem{Patrick2015}
Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.

%43
\bibitem{Cormem}
Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.

%44
\bibitem{Holzmann11}
Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.

>>>>

\comment{In any HW and SW design of complex systems, more time is spent on verification than on construction~\cite{Baier2008}. Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Software (and systems) may be viewed as mathematical objects with behavior that is, in principle, well determined. This makes it possible to specify software using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the software meets its specification ~\cite{Clarke2009}. Research in formal methods has led to the development of very promising verification techniques, which facilitate the early detection of errors. Model-based verification techniques use models that describe the possible system behavior in a mathematically precise and unambiguous manner. The system models are accompanied by algorithms that systematically explore all the states of the system model.}

@@

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3. All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.

@@

\comment{
Model checking refers to algorithms for exploring the state space of a transition system to determine if it obeys a speciﬁcation of its intended behavior~\cite{Baier2008}, ~\cite{Clarke2009}. These algorithms can perform exhaustive exploration in a highly automatic way and, thus, have attracted much interest in industry. However, model-checking has been held back by the state explosion problem, in which the number of states in a system grows exponentially in the number of system components ~\cite{Biere2009}. Much research has been devoted to mitigate this problem.
}

@@

The basic idea of BMC is to check the negation of a given property at a given depth: given a transition system $M$, a property $\phi$, and a bound $k$, BMC unrolls the system $k$ times and translates it into a verification condition (VC) $\psi$  such that $\psi$ is satisfiable if and only if $\phi$ has a counterexample of depth $k$ or less~\cite{Biere2009}. To cope with increasing software complexity, SMT solvers can be used as back-ends for solving the generated VCs, as shown in~\cite{Cordeiro2012},~\cite{Armando2009},~\cite{Ganai2006}.

@@

Algorithm~\ref{vZ-pseudocode} encodes the objective function and constraints related to the HW-SW partitioning problem using $\nu$Z functions~\cite{Bjorner2014}. A $\nu$Z logical context must firstly be created (line $2$), in order to add constraints and to check whether a given model exists to the set of constraints. Note that the number of nodes and edges, software, hardware, and communications costs as well as the incidence matrix E must also be declared.

@@

%3
\bibitem{Trindade2015}
Trindade, A., Cordeiro. L. (2015), ``{Applying SMT-based verification to hardware/software partitioning in embedded systems,}'' In: Design Automation for Embedded Systems (to appear).

%4
\bibitem{Trindade2016}
Trindade, A. B., Ismail, H. I., Cordeiro, L. C. (2015), ``{Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems (short paper),}'' To appear in V Brazilian Symposium on Computing Systems Engineering (SBESC), pp. 1-4.

%5
\bibitem{Bjorner2015}
Bjorner, N., Phan, A-D., Fleckenstein, L. (2015), ``{$\nu$Z - An Optimizing SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 194--199.

%6
\bibitem{Tang2009}
Tang, T., Lin, Y., Ren, X. (2010), ``{Mapping OpenMP concepts to the stream programming model. In: Proc. of the Intl. Conf. on Computer Science Education},'' pp. 1900--1905.

%7
\bibitem{OpenMP1998}
OpenMP Architecture Review Board, OpenMP C and C++
Application Pogram Interface, Version 1.0, October 1998.
http://www.openmp.org

%8
\bibitem{Cordeiro2012}
Cordeiro, L., Fischer, B., Marques-Silva, J. (2012), ``{SMT-based Bounded Model Checking for Embedded ANSI-C Software},'' In: IEEE Transactions on Software Engineering, v. 38, n. 4, pp. 957--974.

@@

%10
\bibitem{Biere2009}
Biere, A. (2009), ``{Bounded Model Checking. In: Biere, A., Heule, M., van Marren, H., Walsh, T. (org.)}'', Handbook of Satisfiability, IOS Press, pp. 457–-481.

%11
\bibitem{Armando2009}
Armando, A., Mantovani, J., Platania, L. (2009), ``{Bounded model checking of software using SMT solvers instead of SAT solvers},'' In: Intl. Journal on Software Tools for Technology Transfer, v. 11, n. 1, pp. 69--83.

%12
\bibitem{Ganai2006}
Ganai, M., Gupta, A. (2006), ``{Accelerating high-level bounded model checking},'' In: Proc. of the IEEE/ACM Intl. Conf. on Computer-Aided Design, pp. 794-–801.

%13
\bibitem{Ramalho2013}
Ramalho, M., Freitas, M., Souza, F., Marques, H., Cordeiro, L. (2013), ``{SMT-Based Bounded Model Checking of C++ Programs.},'' In: Intl. Conf. and Workshops on the Engineering of Computer-Based Systems, pp. 147--156.

%14
\bibitem{DeMoura2008}
De Moura, L., Bjorner, N. (2008), ``{Z3: An Efficient SMT Solver},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 4963, pp. 337–-340.

%15
\bibitem{Brummayer2009}
Brummayer, R., Biere, A. (2009), ``{Boolector: An Efficient SMT Solver for Bit-Vectors and Arrays.},'' In: Proc. of the Intl. Conf. on Tools and Algorithms for the Construction and Analysis of Systems, LNCS 5505, pp. 174-–177.

%16
\bibitem{Barrett2011}
Barrett, C., Conway, C. Deters, M., Hadarean, L., Jovanovic, D., King, T., Reynolds, A., Tinelli, C. (2011), ``{CVC4},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 6806, pp. 171--177.

%17
\bibitem{Bozzano2005}
Bozzano, M., Bruttomesso, R., Cimatti, A., Junttila, T., Rossum, P., Schulz, S., Sebastiani, R. (2005), ``{MathSAT: Tight integration of SAT and mathematical decision procedures},'' In: Journal of Automated Reasoning, v. 35, n. 1-3, pp. 265--293.

%18
\bibitem{Dutertre2014}
Dutertre, B. (2014), ``{Yices 2.2. In: Proc. of the Intl. Conf. on Computer-Aided Verification},'' LNCS 8559, pp. 737–-744.

%19
\bibitem{Wu2014}
Wu, M., Wu, W., Tai, N., Zhao, H., Fan, J., Yuan, N. (2014), ``{Research on OpenMP model of the parallel programming technology for homogeneous multicore DSP},'' In: Proc. of the Intl. Conf. on Software Engineering and Service Science, pp. 921--924.

%20
\bibitem{Bjorner2014}
Bjorner, N. and Phan, A. D. (2014), ``{$\nu$Z - Maximal Satisfaction with Z3},'' In: Proc. of the Intl. Symp. on Symbolic Computation in Software Science, pp. 1--10.

%21
\bibitem{Federica2008}
Federica, P., Rodolfo, F., Yuqing , S., Elisa, B. (2008), {``Authorization and User Failure Resiliency for WS-BPEL business processes''}, In: Proc. of the Intl. Conf. on Service-Oriented Computing, LNCS 5364, pp. 116--131

%22
\bibitem{NarodytskaN}
Narodytska, N., Bacchus, F. (2014), {``Maximum Satisfiability Using Core-Guided MAXSAT Resolution},'' In: Proc. of the AAAI Conf. on Artificial Intelligence, pp. 2717--2723.

%23
\bibitem{Barth1995}
Barth, P., Davis-Putnam, A. (1995), {``Enumeration Algorithm for Linear
Pseudo-Boolean Optimization.''}, Technical Report MPI-I-95-2-003, Max Plank Institute for Computer Science.

%24
\bibitem{Vasco2005}
Vasco, M., Marques-Silva, J. (2005), {``Effective Lower Bounding Techniques for Pseudo-Boolean Optimization''}, IST/INESC-ID, Technical University of Lisbon, Portugal.

%25
\bibitem{Z3API}
Magellan, ``{Source code and documentation},''
  \url{https://github.com/Z3Prover/z3}, Accessed 18th August 2015.

%26
\bibitem{Cormem}
Cormen, T., Leiserson, C., Rivest, R., Stein, C. (2009), {``Introduction to Algorithms''}, MIT Press, pp. I-XIX, pp. 1--1292.

%27
\bibitem{Dagum1998}
Dagum, L., Menon, R. (1998), ``{OpenMP: An Industry-Standard API for Shared-Memory Programming.},'' In: Proc. of the Intl. Conf. on Computational Science \& Engineering, v. 5, n. 1, pp. 46--55.

%28
\bibitem{TheMathWorks2013}
The MathWorks, Inc. (2013), ``{MATLAB (version R2013a)}'', Natick, MA.

%29
\bibitem{Tranquillo2011}
Tranquillo, J. (2011), ``{Matlab for Engineering and the Life Sciences}'', Synthesis Lectures on Engineering. Morgan \& Claypool.

%30
\bibitem{Hong2010}
Hong, L., Cai, J. (2010), ``{The application guide of mixed programming between MATLAB and other programming languages},'' In: Proc. of the Intl. Conf. on Computer and Automation Engineering, pp. 185--189.

%31
\bibitem{Cordeiro2011}
Cordeiro, L., Fischer, B. (2011), ``{Verifying multi-threaded software using SMT-based context-bounded model checking.},'' In: Proc. of the Intl. Conf. on Software Engineering, pp. 331--340.

%32
\bibitem{Teich2012}
Teich, J. (2012), ``{Hardware/Software Codesign: The Past, the Present, and Predicting the Future},'' In: Proc. of the IEEE, Special Centennial Issue, v. 100, pp. 1411--1430.

%33
\bibitem{Guthaus2001}
Guthaus, M., Ringenberg, J., Ernst, D., Austin, T., Mudge, T., Brown, R. (2001), ``{MiBench: a free, commercially representative embedded benchmark suite},'' In: Proc. of the annual workshop on workload characterization, pp. 3--14.

%34
\bibitem{Arato2005}
Arat\'o, P., Mann, Z.A., Orb\'an, A. (2005), ``{Algorithmic aspects of hardware/software partitioning.},'' Transactions on Design Automation of Electronic Systems, v. 1, pp. 136–-156.

%35
\bibitem{Holzmann2011}
Holzmann, G.J., Joshi, R., Groce, A. (2011), ``{Swarm Verification Techniques},'' In: IEEE Transactions on Software Engineering, v. 37, n. 6, pp. 845--857.

%36
\bibitem{Holzmann2012}
Holzmann, G. (2012), ``{Parallelizing the spin model checker. In: Proc. of the Intl. Symp. on Model Checking Software},'' LNCS 7385, pp. 155--171.

%37
\bibitem{Wintersteiger2009}
Wintersteiger, C., Hamadi, Y., De Moura, L. (2009), ``{A Concurrent Portfolio Approach to SMT Solving.},'' In: Proc. of the Intl. Conf. on Computer-Aided Verification, LNCS 5643, pp. 715--720.

%38
\bibitem{Qawasmeh2014}
Qawasmeh, A., Malik, A., Chapman, B. (2014), ``{OpenMP task scheduling analysis via OpenMP runtime API and tool visualization.},'' In: Proc. of the Intl. Symp. on Parallel \& Distributed processing, pp. 1049--1058.

%39
\bibitem{Pavlinovic2015}
Pavlinovic, Z., King, T., Wies, T. (2015),{``Practical SMT-Based Type Error Localization''}, In: Proc. of the Intl. Conf. on Functional Programming, pp. 412--423.

%40
\bibitem{Patrick2015}
Sebastiani, R., Trentin, T. (2015), {``OptiMathSAT: A Tool for Optimization Modulo Theories''}, In: Proc. of the Intl. Conf. on Computer Aided Verification, LNCS 9206, pp. 447--454.

%41
\bibitem{Holzmann11}
Gerard J. Holzmann, Rajeev Joshi, Alex Groce (2011), {``Swarm Verification Techniques''}, In: IEEE Trans. Software Eng. v. 37, n. 6, pp. 845--857.
